IML Term project

### 2022-11-23 main_markdown.rmd
Update main_markdown.rmd
Sara testaa Naive Bayesia.

>>>>

```{r functions}

# mean squared error
mse <- function(yhat, y) sqrt(mean((y - yhat)**2))

# classification accuracy
cacc <- function(pred, true) sum(as.integer(as.logical(pred == true)))/length(pred)

# cross-validate
# split n items into k folds of roughly equal size
kpart <- function(n, k) {
    rep_len(1:k, length.out = n)
}

# Find cross-validation predictions
cv <- function(
               formula, # Formula specifying which variables to use
               data, # Dataset
               model = lm, # Type of model to train (as a function)
               n = nrow(data), # number of rows in the data matrix
               k = min(n, 20), # number of cross-validation folds
               split = kpart(n, k), # the split of n data items into k folds
               ## function to train a model on data
               train = function(data) model(formula, data = data),
               ## function to make predictions on the trained model
               pred = function(model, data) predict(model, newdata = data)) {
    yhat <- NULL
    for (i in 1:k) {
        ## go through all folds, train on other folds, and make a prediction
        mod <- train(data[split != i, ])
        if (is.null(yhat)) {
            ## initialise yhat to something of correct data type,
            yhat <- pred(mod, data)
        } else {
            yhat[split == i] <- pred(mod, data[split == i, ])
        }
    }
    yhat # finally, output cross-validation predictions
}

loocv <- function(
               formula, # Formula specifying which variables to use
               data, # Dataset
               model = lm, # Type of model to train (as a function)
               ## function to train a model on data
               train = function(data) model(formula, data = data),
               ## function to make predictions on the trained model
               pred = function(model, data) predict(model, newdata = data)) {
    yhat <- NULL
    for (i in 1:nrow(data)) {
        ## go through all stations, train on other stations, and make a prediction
        mod <- train(data[-i, ])
        if (is.null(yhat)) {
            ## initialise yhat to something of correct data type,
            yhat <- pred(mod, data)
        } else {
            yhat[i] <- pred(mod, data[i, ])
        }
    }
    yhat # finally, output cross-validation predictions
}

# Classifiers

## Testing classifiers as they are

```{r naive bayes}

library(e1071)

idx <- sample(nrow(npf), nrow(npf)/2)
npf_train <- npf[idx, ]
npf_test <- npf[-idx, ]

# nb.fit <- naiveBayes(class2 ~ . , data = npf_train)

a <- data.frame(train = cacc(predict(nb.fit, newdata = npf_train), npf_train$class2),
                test = cacc(predict(nb.fit, newdata = npf_test), npf_test$class2),
                CV = cacc(cv(class2 ~ ., npf_train, naiveBayes), npf_train$class2),
                LOOCV = cacc(loocv(class2 ~ ., npf_train, naiveBayes), npf_train$class2))
a
